Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
Adds some straw man examples to section 4

So called ``bolt-on'' services are third-party solutions integrated into a
system to provide functionality and improve performance for common use-cases
(e.g. a metadata service). The introduction of additional services may provide
simplicity and performance enhancements, but ``bolt-on'' services often
duplicate functionality, unnecessarily increasing the likelihood of bugs or
introducing unpredictable performance problems. For example, we are developing
a high-performance distributed shared-log on Ceph called ZLog, based on the
CORFU protocol~\cite{corfu}. Without going into greater detail, the CORFU protocol by separating the concern of correctness from the concern of performance enables serialization using a \emph{volatile}
``sequencer'' service. This high-performance in-memory counter is used to assign a log
position to each client that appends to the log. The sequencer is purely a performance optimization and does not have a role in correctness (if the sequencer fails, the tail of the log can always be retrieved by other means). Thus, it is the volatility of the sequencer that enables high performance. A ``bolt-on'' option for building
a distributed log is to use PAXOS, or an out-of-the-box solution such as
Zookeeper. However, these systems adhere to the preconceived notions of
storage, namely that data is safe from data loss, which is exactly the feature
that causes traditional approaches to run at significantly reduced speed.

@@

Ceph is a production-quality distributed system and in this section we
touch on some of the subsystems it uses to provide a general-purpose
storage system. In the next section, we describe how we leverage these
subsystems to build new services. This is the an exhuastive list of services.

@@

A consistent view of cluster state among Ceph daemons and clients is critical
to provide strong consistency guarantees to clients.  Ceph maintains cluster
state information in per-subsystem ``maps'' (e.g. OSD map, MDS map) that
record membership and status information. A PAXOS-based monitoring service is
responsible for integrating state changes into cluster maps, and responding to
requests from out-of-date clients.  As a fundamental building block of many
system designs, consensus abstractions such as PAXOS are a common technique
for maintaining consistent data versions, and are a useful system to expose.
While Ceph does not expose this service directly, it does allow limited use by
clients through a key-value service intended for low-volume, small size
configuration information.

@@

Ceph provides a rich plugin framework for defining new interfaces to objects
stored within RADOS, effectively allowing developers to use co-design
techniques to define logical storage devices tailored to their application
domain.

@@

Mantle is a framework that allows balancing policies to be written in Lua,
and supports such policies be specified at run-time.

@@

Mantle~\cite{sevilla:sc15-mantle} is a programmable metadata
balancer for Ceph that separates the metadata balancing policies from their
mechanisms. Administrators inject code to change how the metadata cluster
distributes metadata. In the paper, we showed how to implement a single
node metadata service, a distributed metadata services with hashing, and
a distributed metadata service with dynamic subtree ipartitioning.

@@

We implemented it using the components from section 3. I will tell you about them here.

>>>>

So called ``bolt-on'' services are third-party solutions integrated into a
system to provide functionality and improve performance for common use-cases
(e.g. a metadata service). The introduction of additional services may provide
simplicity and performance enhancements, but ``bolt-on'' services often
duplicate functionality, unnecessarily increasing the likelihood of bugs or
introducing unpredictable performance problems. For example, we are developing
a high-performance distributed shared-log on Ceph called ZLog, based on the
CORFU protocol~\cite{corfu}. Without going into greater detail, the CORFU protocol, by separating the concern of correctness from the concern of performance, enables serialization using a \emph{volatile}
``sequencer'' service. This high-performance in-memory counter is used to assign a log
position to each client that appends to the log. The sequencer is purely a performance optimization and does not have a role in correctness (if the sequencer fails, the tail of the log can always be retrieved by other means). Thus, it is the volatility of the sequencer that enables high performance. A ``bolt-on'' option for building
a distributed log is to use PAXOS, or an out-of-the-box solution such as
Zookeeper. However, these systems adhere to the preconceived notions of
storage, namely that data is safe from data loss, which is exactly the feature
that causes traditional approaches to run at significantly reduced speed.

@@

Ceph is a production-quality distributed storage system and in this section we
touch on some of the subsystems it uses to provide a general-purpose
storage system. In the next section, we describe how Malacology exposes these
subsystems in order to enable the creation of new services.

@@

% straw man example
Keeping track of the state of a distributed system is an essential part of any 
successful service and a necessary component in order to diagnose and detect 
failures, when they occur. In the case of Ceph, a consistent view of cluster 
state among server daemons and clients is critical
to provide strong consistency guarantees to clients. Ceph maintains cluster
state information in per-subsystem ``maps'' (e.g. OSD map, MDS map) that
record membership and status information. A PAXOS-based monitoring service is
responsible for integrating state changes into cluster maps, and responding to
requests from out-of-date clients. As a fundamental building block of many
system designs, consensus abstractions such as PAXOS are a common technique
for maintaining consistent data versions, and are a useful system to expose.
While Ceph does not expose this service directly, it does allow limited use by
clients through a key-value service intended for low-volume, small size
configuration information.

@@

Allowing users to define custom code that executes in the storage nodes is a 
useful technique for offloading computation closer to where the data is stored 
in order to significantly reduce the amount of data moved between storage 
servers and clients. Ceph provides a rich plugin framework for defining new 
interfaces to objects
stored within RADOS, effectively allowing developers to use co-design
techniques to define logical storage devices tailored to their application
domain.

@@

@@

Mantle~\cite{sevilla:sc15-mantle} is a programmable metadata
balancer for Ceph that separates the metadata balancing policies from their
mechanisms. Administrators inject code to change how the metadata cluster
distributes metadata. In ~\cite{sevilla:sc15-mantle} the authors showed how 
using Mantle, one can implement a single node metadata service, a distributed 
metadata services with hashing, and a distributed metadata service with dynamic 
subtree partitioning.

@@

Mantle is a framework that allows balancing policies to be written in Lua,
and supports such policies be specified at run-time.
We implemented it using the components from section 3. I will tell you about them here.
